\section{Future Work}
While the Personal Finance Manager application meets the core requirements outlined in the project specification, there are several areas for potential enhancement and future development:
\begin{itemize}
\item \textbf{Graphical User Interface (GUI)} - Transitioning from a console-based interface to a graphical user interface would significantly improve user experience. A
GUI could provide intuitive navigation, visual charts for financial data, and drag-and-drop functionality for managing transactions and wallets.
\item \textbf{Multi-User Support} - Implementing multi-user capabilities would allow different users to maintain separate financial records within the same application instance. This could involve user authentication, profile management, and data isolation. 
\item \textbf{Cloud Synchronization} - Adding cloud synchronization features would enable users to back up their data online and access it from multiple devices. This could involve integrating with cloud storage services or developing a custom backend server for data management.
\item \textbf{Mobile Application} - Developing a mobile version of the Personal Finance Manager would allow users to manage their finances on-the-go. A mobile app could leverage device features such as notifications for upcoming bills or expenses. 
\end{itemize}
These enhancements would not only broaden the application's functionality but also improve its accessibility and user engagement, making it a more comprehensive tool for personal finance management.