\section{Project Overview}

\subsection{Introduction}
The \textbf{Personal Finance Manager} is a cross-platform console application developed in C++ to help users track their financial health. It enables the efficient management of multi-wallet balances, income and expense records, and automated recurring transactions through a command-line interface.

\subsection{Key Technical Highlights}
This project was engineered under a strict academic constraint: \textbf{No Standard Template Library (STL)} was permitted. To achieve this, we implemented:
\begin{itemize}
    \item \textbf{Custom Data Structures:} Generic \texttt{ArrayList} and \texttt{HashMap} containers built from scratch using manual memory management (pointers).
    \item \textbf{MVC Architecture:} A strict separation of Data (Models), Business Logic (AppController), and User Interface (ConsoleView) to ensure scalability.
    \item \textbf{Persistence \& Auto-Save:} A custom binary serialization engine coupled with a \textbf{multi-threaded background worker} that automatically persists data changes to disk, ensuring zero data loss.
    \item \textbf{Cross-Platform Support:} Universal build scripts (\texttt{.bat} and \texttt{.command}) ensuring seamless execution on both Windows and macOS.
\end{itemize}

\subsection{Objectives}
The main objectives of the Personal Finance Manager project are:
\begin{itemize}
  \item Provide a reliable and easy-to-use command-line interface for tracking personal finances (wallets, incomes, expenses, recurring transactions).
  \item Ensure data integrity and persistence through robust serialization and safe update/delete semantics (restrict-delete checks and immediate save for critical operations).
  \item Keep business logic centralized and testable (single `AppController` entry point) and provide small, single-responsibility UI flows for easy validation.
  \item Support cross-platform execution and reproducible builds so evaluators can run the application on Windows and macOS with minimal setup.
  \item Produce clear documentation, diagrams and screenshot evidence so graders can verify implemented features quickly.
\end{itemize}

\subsection{Scope}
This project is scoped as a single-user, desktop console application. The scope includes:
\begin{itemize}
  \item Core features: create/view/edit/delete transactions (income/expense), manage wallets, categories and income sources, recurring transaction automation, and basic reporting (monthly summaries, category breakdowns).
  \item Presentation: Console UI components (menus, dashboard, tables) and input validation helpers.
  \item Persistence: Binary serialization for saving/loading state and utilities for file IO.
  \item Documentation: A report with diagrams and screenshots; code comments and README for reproducibility.
\end{itemize}

\paragraph{Out of scope}
\begin{itemize}
  \item Multi-user or networked synchronization, central server components, or database-backed services.
  \item Advanced analytics (forecasting, machine learning) or third-party payment integrations.
  \item A graphical desktop/mobile UI — the project intentionally targets the console environment.
\end{itemize}