\section{Requirements Specification}

The system was designed to strictly adhere to the functional specifications outlined in the Final Project Coursework, while satisfying rigorous technical constraints regarding memory management and platform compatibility.

\subsection{Functional Requirements}

\subsubsection{Transaction Management}
The core function of the application is to record and manage financial activities with precision \cite{project_spec}.
\begin{itemize}
    \item \textbf{Income Recording:} Users can log earnings by specifying the Date, Amount, Wallet, and an \textbf{Income Source} (e.g., Salary, Bonus).
    \item \textbf{Expense Recording:} Users can log expenditures by linking them to a \textbf{Category} (e.g., Food, Rent) and a specific Wallet.
    \item \textbf{Validation:} The system must prevent invalid entries, such as negative amounts or linking transactions to non-existent wallets.
\end{itemize}

\subsubsection{Automation (Recurring Transactions)}
To reduce manual data entry, the system supports an automation engine for regular payments.
\begin{itemize}
    \item \textbf{Scheduling:} Users can define templates for recurring transactions (Daily, Weekly, Monthly).
    \item \textbf{Auto-Generation:} Upon application startup, the \texttt{AppController} detects due transactions based on the last generation date and automatically creates the necessary records for the missed period.
\end{itemize}

\subsubsection{Search \& Reporting}
The application provides tools to analyze financial health:
\begin{itemize}
    \item \textbf{Date Range Filtering:} View detailed transaction history within a specific start and end date.
    \item \textbf{Advanced Search:} Filter transactions by Wallet, Category, or Keyword search (in descriptions).
    \item \textbf{Financial Summary:} Aggregated views of Total Income, Total Expense, and Net Balance per Wallet.
\end{itemize}

\subsection{Non-Functional Requirements}

\subsubsection{Technical Constraints (No STL)}
As a primary academic challenge, the use of the **Standard Template Library (STL)** was strictly prohibited for data containers.
\begin{itemize}
    \item \textbf{Implementation:} We replaced \texttt{std::vector} and \texttt{std::map} with custom-built \texttt{ArrayList<T>} and \texttt{HashMap<K,V>} classes using manual dynamic memory allocation.
\end{itemize}

\subsubsection{Data Persistence \& Reliability}
\begin{itemize}
    \item \textbf{Binary Storage:} All data (Transactions, Wallets, Master Data) is serialized to binary files to ensure efficient storage and fast loading times.
    \item \textbf{Auto-Save (Enhancement):} Beyond standard session saving, we implemented a **background thread** that triggers a save operation every 60 seconds. This ensures data integrity even in the event of an unexpected application crash.
\end{itemize}

\subsubsection{Cross-Platform Compatibility}
The application is designed to function identically on different operating systems:
\begin{itemize}
    \item \textbf{Windows:} Compiled via MinGW or Visual Studio (`run_windows.bat`).
    \item \textbf{macOS/Linux:} Compiled via Clang/GCC (`run_mac.command`).
\end{itemize}